---
title: "Coding_Exercises"
author: "Maya"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("setup.R")
```
Load data set:
```{r}
data("knz_bison")
colnames(knz_bison)
```

1. Create a new column in the bison dataset that calculates the individual’s age at the time of observation.
```{r}
knz_bison$animal_age <- knz_bison$rec_year - knz_bison$animal_yob
```

2. Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).
```{r}
filter_bison_weight <- function(data, weight_threshold) {data %>%
    filter(animal_weight >= weight_threshold)}
```
```{r}
heavy_bison <- filter_bison_weight(knz_bison, 500)
```

3. Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.
```{r}
# Find units used for animal weights for accurate labeling:
?knz_bison
```
```{r}
ggplot(knz_bison, aes(x = animal_sex, y = animal_weight, fill = animal_sex)) + geom_boxplot() + labs(title = "Bison Weight Distribution by Sex", x = "Sex", y = "Weight (lbs)") + theme_gray()
```
Male bison have a larger distribution of weights than females, with some outliers nearing/over 2000lbs. Females have a greater lower and upper quartiles, and greater median bodyweight than males. 
```{r}
t_test <- t.test(animal_weight ~ animal_sex, data = knz_bison)
t_test
```
Weight is significantyl different (p < 0.05) between sex of Bisons, where females have a greater mean weight (761.9 lbs) compared to males (727.9 lbs). 
